DATA 624 Homework 5

### 2020-03-07 DATA624/HW5.Rmd
Finalized HW5

>>>>

```{r}
# Window doesn't return a ts object so we need to redefine
retail_train <- ts(as.vector(retail_ts), start=c(1982,4), end=c(2010,12), frequency = 12)
# Get the optimal lambda
lambda <- BoxCox.lambda(retail_train)
# Preform a Box-Cox transformation
bc_retail_train <- BoxCox(retail_train, lambda = lambda)
# Preform the STL decomposition
stl_retail_train <- mstl(bc_retail_train)
## Create a seasonally adjusted series
sa_stl_retail_train <- stl_retail_train[,1] - stl_retail_train[,3]
# Reverse the Box-Cox transformation
sa_retail_train <- InvBoxCox(sa_stl_retail_train, lambda = lambda)
# Check the output
autoplot(retail_train) + autolayer(sa_retail_train)
```
```{r}
ets_retail_train <- forecast(sa_retail_train)

rmse_df %>%
  mutate(Model = as.character(Model)) %>%
  rbind(c("ETS on STL Seasonally-Adjusted data", get_retail_test_rmse(ets_retail_train))) %>%
  kable() %>%
  kable_styling()
```

**The ETS model on the transformed data preformed worse than the Seasonal Naïve model.  Again a simpler approach can be a better one.**
